---
title: "Comparing Statistical Distributions App"
author: "Leandro Zappani"
date: "February 2, 2020"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This simple app allows statistics students to grasp differences and similarities between some discrete and continuous statistical distributions, their parameters, and test the assumptions for the approximations between them.

The app can be accessed using [this link](https://leandrozappani.shinyapps.io/comparing_statistical_distributions/)

## General View

As you can see, in the side panel there are a number of slides and boxes to tweak.

```{r , fig.height = 5, echo = FALSE}
library(png)
library(grid)
img1 <- readPNG("images/app1.png")
grid.raster(img1)
```



***
And in the bottom part there is some instructions.

```{r , fig.height = 5, echo = FALSE}
img2 <- readPNG("images/app2.png")
grid.raster(img2)
```

## Example of usage
One approximation learned in introductory statistics is that with large n and probability of success close to 0.5, the binomial distribution can be approximated by a normal distribution.

```{r , fig.height = 5, echo = FALSE}
img3 <- readPNG("images/app3.png")
grid.raster(img3)
```

In this example, the parameters for the binomial are $p=0.5$ and $n=20$, so the mean is $\overline x =p n=10$ and standard deviation is $s= \sqrt{p(1-p) n }\approx 2.24$. When we tweak the normal parameters accordingly, the distritions match.


